Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants

### 2017-01-24 cav2017/cav2017.tex
moved contributions

@@

Program synthesizers are an ideal fit for synthesis of %parametric
digital controllers, since the semantics of programs capture effects such as FWL
precisely.  In~\cite{DBLP:conf/cdc/RavanbakhshS15}, the authors use CEGIS
for the synthesis of switching controllers for stabilizing continuous-time
plants with polynomial dynamics.  The work extends to affine systems, 
finding a major challenge in the hardness of solving linear arithmetic with the state-of-the-art SMT solvers.  
Since this approach uses switching models instead of linear dynamics for the digital controller, 
it entirely circumvents the FWL problem, but potentially incurs state-space explosion issues.  
This approach is not suitable for the kind of control we seek to synthesize.

%\textcolor{red}{Cristina: can you please revise this sentence:
Moreover, in \cite{DBLP:conf/emsoft/RavanbakhshS16} the same authors 
use a CEGIS-based approach for synthesizing continuous-time switching
controllers that guarantee \emph{reach-while-stay} properties of closed-loop systems, 
i.e., properties that specify a set of goal states and safe states (constrained reachability).%}. 
The solution is based on synthesizing control Lyapunov 
functions for switched systems, that yield switching controllers with
a guaranteed minimum dwell time in each mode.

The work in \cite{DBLP:journals/corr/AbateBCCDKK16} investigates the synthesis of 
stabilizing controllers for continuous plants described as transfer functions, 
by exploiting bit-accurate verification of software-implemented 
digital controllers~\cite{Bessa16}.  While this work also make use of a CEGIS-based technique, 
the approach is restricted to synthesizing digital controllers for stable 
closed-loop systems described via transfer function models.  
In contrast, in the current paper we consider a state-space representation of the physical system, 
which is known to be more general \cite{Astrom08} and allows to synthesize controllers that
make the closed-loop system \emph{safe}.  Moreover, 
this work  integrates an abstraction/refinement step inside the main CEGIS loop.

@@

We use a combination of a synthesis engine with a control
verification tool that addresses the challenges presented in the
form of FWL effects and stability measures over digital controllers for LTI models.

We take the synthesis engine from~\cite{DBLP:conf/lpar/DavidKL15}. The verification engine, for
the first approach we present, performs bounded model checking of control properties,
based on~\cite{Monteiro16}, but enhanced to include evaluation of quantization effects and safety properties
over the state space. In an alternative approach, we use a verification engine based on abstract acceleration~\cite{cattaruzza2015unbounded}, 
which avoids the explicit unwinding the transition system necessarily for the first approach.

>>>>

\textit{Contributions}. We use a combination of a synthesis engine with a control
verification tool that addresses the challenges presented in the
form of FWL effects and stability measures over digital controllers for LTI models.  
We take the synthesis engine from~\cite{DBLP:conf/lpar/DavidKL15}. The verification engine, for
the first approach we present, performs bounded model checking of control properties,
based on~\cite{Monteiro16}, but enhanced to include evaluation of quantization effects and 
safety properties over the state space. In an alternative approach, we use a verification engine based 
on abstract acceleration~\cite{cattaruzza2015unbounded}, which avoids the explicit unwinding 
the transition system necessarily for the first approach.

@@

Program synthesizers are an ideal fit for synthesis of %parametric
digital controllers, since the semantics of programs capture effects such as FWL
precisely.  In~\cite{DBLP:conf/cdc/RavanbakhshS15}, the authors use CEGIS
for the synthesis of switching controllers for stabilizing continuous-time
plants with polynomial dynamics.  The work extends to affine systems, 
finding a major challenge in the hardness of solving linear arithmetic with the state-of-the-art SMT solvers.  
Since this approach uses switching models instead of linear dynamics for the digital controller, 
it entirely circumvents the FWL problem, but potentially incurs state-space explosion issues.  
Moreover, in \cite{DBLP:conf/emsoft/RavanbakhshS16} the same authors 
use a CEGIS-based approach for synthesizing continuous-time switching
controllers that guarantee \emph{reach-while-stay} properties of closed-loop systems, 
i.e., properties that specify a set of goal states and safe states (constrained reachability).
This solution is based on synthesizing control Lyapunov 
functions for switched systems, that yield switching controllers with
a guaranteed minimum dwell time in each mode. However, both approaches 
are not suitable for the kind of control we seek to synthesize.

The work in \cite{DBLP:journals/corr/AbateBCCDKK16} investigates the synthesis of 
stabilizing controllers for continuous plants described as transfer functions, 
by exploiting bit-accurate verification of software-implemented 
digital controllers~\cite{Bessa16}.  While this work also makes use of a CEGIS-based technique, 
the approach is restricted to synthesizing digital controllers for stable 
closed-loop systems described via transfer function models.  
In contrast, in the current paper we consider a state-space representation of the physical system, 
which is known to be more general \cite{Astrom08} and allows to synthesize controllers that
make the closed-loop system \emph{safe}.  Moreover, 
this work  integrates an abstraction/refinement step inside the main CEGIS loop.

@@
